---
title: "brand_prediction"
author: "Ashiqur"
date: "10/17/2019"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(echo = TRUE)
```

## Loading data sets and libraries
```{r data_lib,echo=TRUE}
brands_choice <- read.csv(file="Data/CompleteResponses_train.csv", header = TRUE )
brands_incomplete<-read.csv(file = "Data/SurveyIncomplete_test.csv", header = TRUE)

library(caret)
library(dplyr)
library(C50)
library(ggplot2)


```
## Renaming attributes
```{r rename, echo=TRUE}
names(brands_choice) <- 
  c("salary","age","education","car","zip","credit","brand")

names(brands_incomplete) <- 
  c("salary","age","education","car","zip","credit","brand")
```

## changing name of the brands
```{r pls_model, echo=TRUE}

brands_choice[which(brands_choice$brand == 0),]$brand = "Belkin"
brands_choice[which(brands_choice$brand == 1),]$brand = "Elago"

```

## preprocess
```{r basic exploration}
summary(brands_choice)
```


## feature selection
```{r fselection,echo=TRUE}
brands_choice_4f <- brands_choice %>% select("salary","age","education","brand")

brands_incomplete_4f <- brands_incomplete %>% select("salary","age","education","brand")
```


## changing Data type
```{r datachanging,echo=TRUE}
brands_choice_4f$brand<-as.factor(brands_choice_4f$brand)

brands_choice_4f$education<-as.factor(brands_choice_4f$education)

brands_incomplete_4f$education<-as.factor(brands_incomplete_4f$education)


```
### Data partition
define 75% train data and 25% test data split from the data set
```{r partition,echo=TRUE}
set.seed(123)#set random seed we can make this analysis repetable
brands_choice_sample <- createDataPartition(brands_choice_4f$brand, p=.75, list = FALSE)


brands_choice_train<-brands_choice_4f[brands_choice_sample,]#traning data 
brands_choice_test<-brands_choice_4f[-brands_choice_sample,]#testing data
brands_choice_train$brand <- as.factor(brands_choice_train$brand)
```

# Machine learning model

### Partial Least Squares Analysis
```{r PLS,echo=TRUE}
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10,
                     repeats = 3)
plsFit <- train(brand~., data=brands_choice_train, 
                method="pls", 
                preProc=c("center","scale"),
                tuneLength = 6,#no changes
                trControl=ctrl)
plsFit
```

## pls MODEL
`
```{r PLOT,echo=TRUE}
ggplot(plsFit) 

```
#PLS model using Metric = ROC
```{r pls_rock,echo=TRUE}
ctrl_roc <- trainControl(method = "repeatedcv", 
                     repeats = 3,
                     number = 10,
                     classProbs=TRUE, 
                     summaryFunction=twoClassSummary)

plsFit_roc <- train(brand~., data=brands_choice_train, 
                method="pls", 
                preProc=c("center","scale"),
                tuneLength = 4,
                trControl=ctrl_roc, 
                metric="ROC")
plsFit_roc
```



## pls plot with roc matric
````{r PLOT_pls,echo=TRUE }
ggplot(plsFit_roc)

```

## Importance of variables
```{r imp_var, echo=TRUE}
varImp(plsFit)
#varImp(plsFit_roc)
```
## Prediction Model(PLS)
```{r pred, echo=TRUE}
plsPred <- predict(plsFit, 
                   newdata = brands_choice_test)
head(plsPred)
postResample(plsPred, brands_choice_test$brand)
summary(plsPred)
```


## Predictions for incomplete data-PLS
```{r Brand_Prediction, echo=TRUE}
brand_plsPred <- predict(plsFit, newdata = brands_incomplete_4f)
summary(brand_plsPred)
barplot(table(brand_plsPred))

```



## Random Forest Analysis

```{r Random_Forest, echo=TRUE}
grid = expand.grid(.mtry = c(2,3))

ctrl <- trainControl(method = "oob" ,
                     search = "grid",
                     classProbs = TRUE
                     )
rfFit <- train(brand~., 
               data=brands_choice_train, 
               method="rf", 
               preProc=c("center","scale"),
               tuneGrid = grid,
               trControl=ctrl
               )
rfFit
ggplot(rfFit)
```


## Importance of variables in RandomForest model

```{r imp_var_rf, echo=TRUE}
varImp(rfFit)
```
## Prediction Model - Random Forest
```{r pred_rf, echo=TRUE}
rfPred <- predict(rfFit, 
                  newdata=brands_choice_test, 
                  type="raw")
summary(rfPred)
head(rfPred)
postResample(rfPred, brands_choice_test$brand)
```


## Predictions for incomplete data  - Random Forest
```{r Brand_Prediction_rf, echo=TRUE}
rfPred <- predict(rfFit, 
                  newdata = brands_incomplete_4f,
                  type = "raw")

summary(rfPred)
barplot(table(rfPred))

```

## decission tree
```{r decission_tree, echo=TRUE}
#crossvalidation technique has been used
ctrl <- trainControl(method = "repeatedcv", 
                     number = 10,
                     repeats = 1,
                     classProbs = TRUE)


#trained the model using decission tree(C5.0)
c50Fit <- train(brand~., 
                data = brands_choice_train,
                method = "C5.0",
                trControl = ctrl,
                metric = "Accuracy", 
                tuneLength = 2,
                preProc = c("center", "scale"))

print(c50Fit)
#confusionMatrix(c50Pred, brands_choice_test$brand)
plot(c50Fit, main="Decision Tree")

saveRDS(c50Fit, "DecTreeModel.rds")
print(c50Fit)

```
## Predictions for incomplete data  - decission Tree
```{r Brand_Prediction_c5, echo=TRUE}
DecTreeModel <- readRDS("DecTreeModel.rds")
#predict  brand  from test data 
DTPredictions <-predict(DecTreeModel, 
                        newdata = brands_choice_test,
                        type = "raw")


summary(DTPredictions)
head(DTPredictions)
postResample(DTPredictions, brands_choice_test$brand)##??

##predict incomplete data

DTPredictions_in <-predict(DecTreeModel, 
                        newdata = brands_incomplete_4f,
                        type = "raw")
barplot(table(DTPredictions_in))
postResample(DTPredictions_in, brands_choice_test$brand)

```
Three models have been chosen to analyze this brand preference and decision tree is the good one as a model if you notice the accuracy.new incomplete data set has been taken as a test data to predict the brand preference and the ELAGO brand has found the most customer preference. Blackwell Electronics can pursue a deeper strategic relationship with ELAGO if you don't consider some other business factors.

